### 2021-12-08 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@a5943ded537de0e77810368ff8ebb79033739ccf 🚀

\hypertarget{effect-of-training-set-on-performance}{%
\subsection{Effect of training set on
performance}\label{effect-of-training-set-on-performance}}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Strydom2021RoaPre}{}%
Strydom, T., Catchen, M. D., Banville, F., Caron, D., Dansereau, G.,
Desjardins-Proulx, P., Forero-Muñoz, N. R., Higino, G., Mercier, B.,
Gonzalez, A., Gravel, D., Pollock, L., \& Poisot, T. (2021). A roadmap
towards predicting species interaction networks (across space and time).
\emph{Philosophical Transactions of the Royal Society B: Biological
Sciences}, \emph{376}(1837), 20210063.
\url{https://doi.org/10.1098/rstb.2021.0063}

>>>>

The training sample is composed of 30\% of the \(4\times 10^4\) possible
entries in the network, \emph{i.e.} \(n=12000\). Out of these
interactions, we pick a proportion \(\nu\) (the training set bias) to be
positive, so that the training set has \(\nu n\) interactions, and
\((1-\nu) n\) non-interactions. We vary \(\nu\) uniformly in \(]0,1[\).
This allows to evaluate how the measures of binary classification
performance respond to artificially rebalanced dataset for a given
network connectance. Note that both \(\xi\) and \(\nu\) are sampled from
a distribution rather than being picked on a grid; this is because there
is no direct relationship between the value of \(\xi\) and the
connectance of the simulated network, and therefore the precise value of
\(\xi\) is not relevant for the analysis of the results.

The dataset used for numerical experiments is composed of 20000 such
\((\xi, \nu)\) pairs, on which four models are trained: a decision tree
regressor, a boosted regression tree, a ridge regressor, and a random
forest regressor. All models were taken from the \texttt{MLJ.jl} package
(Blaom et al., 2020; Blaom \& Vollmer, 2020) in Julia 1.7 (Bezanson et
al., 2017). The complete code to run the simulations is given as an
appendix. \#\# Effect of training set on performance

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-Bezanson2017JulFre}{}%
Bezanson, J., Edelman, A., Karpinski, S., \& Shah, V. (2017). Julia: A
Fresh Approach to Numerical Computing. \emph{SIAM Review}, \emph{59}(1),
65--98. \url{https://doi.org/10.1137/141000671}

\leavevmode\hypertarget{ref-Blaom2020MljJul}{}%
Blaom, A. D., Kiraly, F., Lienart, T., Simillides, Y., Arenas, D., \&
Vollmer, S. J. (2020). MLJ: A Julia package for composable machine
learning. \emph{Journal of Open Source Software}, \emph{5}(55), 2704.
\url{https://doi.org/10.21105/joss.02704}

\leavevmode\hypertarget{ref-Blaom2020FleMod}{}%
Blaom, A. D., \& Vollmer, S. J. (2020, December 31). \emph{Flexible
model composition in machine learning and its implementation in MLJ}.
\url{http://arxiv.org/abs/2012.15505}

\leavevmode\hypertarget{ref-Strydom2021RoaPre}{}%
Strydom, T., Catchen, M. D., Banville, F., Caron, D., Dansereau, G.,
Desjardins-Proulx, P., Forero-Muñoz, N. R., Higino, G., Mercier, B.,
Gonzalez, A., Gravel, D., Pollock, L., \& Poisot, T. (2021). A roadmap
towards predicting species interaction networks (across space and time).
\emph{Philosophical Transactions of the Royal Society B: Biological
Sciences}, \emph{376}(1837), 20210063.
\url{https://doi.org/10.1098/rstb.2021.0063}
